Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression

### 2019-05-01 Manuscript.tex
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:gh-pages

\title{Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression}
\author{Matt Galloway}
\date{2019-04-22}

@@

My parents also deserve a note of appreciation and thanks -- one probably much longer than this. Graduate school's challenges extend far beyond the classroom and I'm so lucky to have you by my side.

@@

Among this community of researchers is Professor Adam Rothman and Aaron Molstad, Ph.D.~whose research will be a focal point of this manuscript. The two have published work on indirect multivariate linear regression (\citet{molstad2016indirect}) and classification with matrix-valued predictors (\citet{molstad2018penalized}) but the focus of this manuscript is their 2017 paper titled \emph{Shrinking Characteristics of Precision Matrix Estimators} (\citet{molstad2017shrinking}). In it, they outline a framework to estimate \emph{characteristics} of precision matrices - a concept that exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature. They write in their manuscript that ``to fit many predictive models, only a characteristic of the population precision matrix needs to be estimated\ldots{} In binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors.'' The purpose of the research detailed here began with the desire to expand on this concept and to explore avenues that were mentioned but were not further investigated.

@@

\begin{equation}
\begin{split}
  l(\Omega | X) &= \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)'\Omega \right] \\
  &= \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
\label{eq:partialmaxloglik}\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
\label{eq:ADMMorig}
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
\label{eq:ZZalgo}
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
  &= \frac{\rho}{2}\left\| R^{k} + \Lambda^{k}/\rho \right\|_{F}^{2} - \frac{\rho}{2}\left\| \Lambda^{k}/\rho \right\|_{F}^{2} \\
  &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
\label{eq:scaled}\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
\label{eq:ADMMscaled}
\end{split}
\end{equation}

@@

Combining these three optimality conditions, Boyd suggests a stopping criterion similar to \(\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}\) and \(\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}\) where \(\epsilon^{rel} = \epsilon^{abs} = 10^{-3}\) and
\begin{equation}
\begin{split}
  \epsilon^{pri} &= p\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| \Omega^{k + 1} \right\|_{F}, \left\| Z^{k + 1} \right\|_{F} \right\} \\
  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \Lambda^{k + 1} \right\|_{F}
\label{eq:admmstopping}\notag
\end{split}
\end{equation}

@@

In their 2017 paper, titled \emph{Shrinking Characteristics of Precision Matrix Estimators}, Aaron Molstad, Ph.D.~and Professor Adam Rothman outline a framework to estimate \emph{characteristics} of precision matrices. This concept, inspired by others like \citet{cai2011direct}, \citet{fan2012road}, and \citet{mai2012direct}, exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature, such as a mean vector. The example they offer in \citet{molstad2017shrinking} is in the context of Fisher's linear discriminant analysis model. If a response vector \(Y\) is categorical such that \(Y\) can take values in \(\left\{1, ..., J\right\}\), then the linear discrimnant analysis model assumes that the design matrix \(X\) conditional on the response vector \(Y\) is normally distributed:

@@

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
\end{align}

@@

\begin{equation}
\begin{split}
  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ g\left(Z^{k}\right) + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)' Q\left(\Omega - \Omega^{k}\right)
\label{eq:approx}
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}\\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
\label{eq:augADMM}\notag
\end{split}
\end{equation}

@@

\begin{equation}
\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
\label{eq:Yk}\notag
\end{equation}
\EndKnitrBlock{theorem}

@@

\begin{equation}
\begin{split}
  \epsilon^{pri} &= \sqrt{nr}\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| A\Omega^{k + 1}B \right\|_{F}, \left\| Z^{k + 1} \right\|_{F}, \left\| C \right\|_{F} \right\} \\
  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2 \right\|_{F}
\label{eq:scpmestopping}\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  l\left( \Omega_{y | x}, \Omega_{x}, \Sigma_{xy} | Y, X \right) &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}'\Omega_{x} X_{i} \right)\left( Y_{i} - \Sigma_{xy}'\Omega_{x} X_{i} \right)'\Omega_{y | x} \right] \\
  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}'\Omega_{x} \right) \\
  &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
  &+ \frac{n}{2}\log\left| \Omega_{x} \right| - \frac{n}{2}tr\left( S_{x}\Omega_{x} \right)
\label{eq:partialjointloglik}\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  \hat{\Omega}_{x} &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S_{x}\Omega_{x} \right) - \frac{n}{2}\log\left| \Omega_{x} \right| \right\} \\
  &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega_{x} \right| + \frac{1}{n}\left\| \left( \mathbb{X}\Omega_{x}\Sigma_{xy} - \mathbb{Y} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
\label{eq:omegajointloglik}\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
\label{eq:appendixomegagradient}\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] \right\} + \nabla_{\Omega}\left\{ tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \lambda(1 - \alpha)Z + \mbox{sign}(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
\label{eq:appendixZZgradient}\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
\label{eq:appendixZZproof}\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z^{k} \right\|_{F}^{2} \right\} \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} + Z^{k + 1} - Z^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) + \rho\left(Z^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} + \rho\left(Z^{k + 1} - Z^{k}\right) \\
  \Rightarrow 0 &\in \rho\left( Z^{k + 1} - Z^{k} \right)
\label{eq:appendixdualresidual}\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k + 1} \right) \right] + \rho\left\| \Omega^{k + 1} - Z^{k + 1} \right\|_{F}^{2} \right\} \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
\label{eq:appendixdualopt}\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)'\left(A'A \otimes BB'\right)vec\left(\Omega - \Omega^{k}\right) \\
  &+ \rho vec\left(\Omega - \Omega^{k}\right)'vec\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right)
\label{eq:taylors}\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  &\nabla_{\Omega}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
  &= 2S - S\circ I_{p} + G^{k} + (G^{k})' - G^{k}\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} \\
  &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})' + 2\Omega' - 2\Omega^{k} - 2(\Omega - \Omega^{k})'\circ I_{p} \right]
\label{eq:appendixomegagradient2}\notag
\end{split}
\end{equation}

>>>>

\title{Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression}
\author{Matt Galloway}
\date{2019-05-01}

@@

My parents also deserve a note of appreciation and thanks -- one probably much longer than this. Graduate school would not have been possible without their love and encouragement.

@@

Among this community of researchers is Professor Adam Rothman and Aaron Molstad, Ph.D.~whose research will be a focal point of this manuscript. The two have published work on indirect multivariate linear regression (\citet{molstad2016indirect}) and classification with matrix-valued predictors (\citet{molstad2018penalized}) but the focus of this manuscript is their 2017 paper titled \emph{Shrinking Characteristics of Precision Matrix Estimators} (\citet{molstad2017shrinking}). In it, they outline a framework to shrink a \emph{characteristic} of a precision matrix - a concept that exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature. They write in their manuscript that ``to fit many predictive models, only a characteristic of the population precision matrix needs to be estimated\ldots{} In binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors.'' The purpose of the research detailed here began with the desire to expand on this concept and to explore avenues that were mentioned but were not further investigated.

@@

\begin{equation}
\begin{split}
  l(\Omega | X) &= \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)'\Omega \right] \\
  &= \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
\end{split}
\label{eq:partialmaxloglik}\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
\end{split}
\label{eq:ADMMorig}
\end{equation}

@@

\begin{equation}
\begin{split}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
\end{split}
\label{eq:ZZalgo}
\end{equation}

@@

\begin{equation}
\begin{split}
  tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
  &= \frac{\rho}{2}\left\| R^{k} + \Lambda^{k}/\rho \right\|_{F}^{2} - \frac{\rho}{2}\left\| \Lambda^{k}/\rho \right\|_{F}^{2} \\
  &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
\end{split}
\label{eq:scaled}\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
\end{split}
\label{eq:ADMMscaled}
\end{equation}

@@

Combining these three optimality conditions, Boyd suggests a stopping criterion similar to \(\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}\) and \(\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}\) where \(\epsilon^{rel} = \epsilon^{abs} = 10^{-3}\) and
\begin{equation}
\begin{split}
  \epsilon^{pri} &= p\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| \Omega^{k + 1} \right\|_{F}, \left\| Z^{k + 1} \right\|_{F} \right\} \\
  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \Lambda^{k + 1} \right\|_{F}
\end{split}
\label{eq:admmstopping}\notag
\end{equation}

@@

In their 2017 paper, titled \emph{Shrinking Characteristics of Precision Matrix Estimators}, Aaron Molstad, Ph.D.~and Professor Adam Rothman outline a framework to shrink a \emph{characteristic} of a precision matrix. This concept, inspired by others like \citet{cai2011direct}, \citet{fan2012road}, and \citet{mai2012direct}, exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature, such as a mean vector. The example they offer in \citet{molstad2017shrinking} is in the context of Fisher's linear discriminant analysis model. If a response vector \(Y\) is categorical such that \(Y\) can take values in \(\left\{1, ..., J\right\}\), then the linear discrimnant analysis model assumes that the design matrix \(X\) conditional on the response vector \(Y\) is normally distributed:

@@

\begin{equation}
\begin{split}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
\end{split}
\label{eq:augmentedprecision}
\end{equation}

@@

\begin{equation}
\begin{split}
  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ g\left(Z^{k}\right) + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)' Q\left(\Omega - \Omega^{k}\right)
\end{split}
\label{eq:approx}
\end{equation}

@@

\begin{equation}
\begin{split}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}\\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
\end{split}
\label{eq:augADMM}\notag
\end{equation}

@@

\begin{equation}
\Lambda^{k + 1} = \Lambda^{k} + \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
\label{eq:Yk}\notag
\end{equation}
\EndKnitrBlock{theorem}

@@

\begin{equation}
\begin{split}
  \epsilon^{pri} &= \sqrt{nr}\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| A\Omega^{k + 1}B \right\|_{F}, \left\| Z^{k + 1} \right\|_{F}, \left\| C \right\|_{F} \right\} \\
  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2 \right\|_{F}
\end{split}
\label{eq:scpmestopping}\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  l\left( \Omega_{y | x}, \Omega_{x}, \Sigma_{xy} | Y, X \right) &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}'\Omega_{x} X_{i} \right)\left( Y_{i} - \Sigma_{xy}'\Omega_{x} X_{i} \right)'\Omega_{y | x} \right] \\
  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}'\Omega_{x} \right) \\
  &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
  &+ \frac{n}{2}\log\left| \Omega_{x} \right| - \frac{n}{2}tr\left( S_{x}\Omega_{x} \right)
\end{split}
\label{eq:partialjointloglik}\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  \hat{\Omega}_{x} &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S_{x}\Omega_{x} \right) - \frac{n}{2}\log\left| \Omega_{x} \right| \right\} \\
  &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega_{x} \right| + \frac{1}{n}\left\| \left( \mathbb{X}\Omega_{x}\Sigma_{xy} - \mathbb{Y} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
\end{split}
\label{eq:omegajointloglik}\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
\end{split}
\label{eq:appendixomegagradient}\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] \right\} + \nabla_{\Omega}\left\{ tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \lambda(1 - \alpha)Z + \mbox{sign}(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
\end{split}
\label{eq:appendixZZgradient}\notag
\end{equation}

@@

\begin{equation}
\begin{split}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
\end{split}
\label{eq:appendixZZproof}\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z^{k} \right\|_{F}^{2} \right\} \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} + Z^{k + 1} - Z^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) + \rho\left(Z^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} + \rho\left(Z^{k + 1} - Z^{k}\right) \\
  \Rightarrow 0 &\in \rho\left( Z^{k + 1} - Z^{k} \right)
\end{split}
\label{eq:appendixdualresidual}\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k + 1} \right) \right] + \rho\left\| \Omega^{k + 1} - Z^{k + 1} \right\|_{F}^{2} \right\} \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
\end{split}
\label{eq:appendixdualopt}\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)'\left(A'A \otimes BB'\right)vec\left(\Omega - \Omega^{k}\right) \\
  &+ \rho vec\left(\Omega - \Omega^{k}\right)'vec\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right)
\end{split}
\label{eq:taylors}\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  &\nabla_{\Omega}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
  &= 2S - S\circ I_{p} + G^{k} + (G^{k})' - G^{k}\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} \\
  &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})' + 2\Omega' - 2\Omega^{k} - 2(\Omega - \Omega^{k})'\circ I_{p} \right]
\end{split}
\label{eq:appendixomegagradient2}\notag
\end{equation}
